Viscous Transport in Eroding Porous Media

### 2019-06-12 docs/transport/erosion_transport.tex
add new figs in transport paper
do the result section in transport paper

{\color{red} the definition of porosity is the ratio 
$$\phi=\frac{A_v}{A_T}$$
where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.
}

@@

In Fig.~\ref{fig:Eroding20tort} we use tortuosity to analysis the effect
of the geometrical structure on fluid velocity field. In
Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the cross section (x=-1
and y in [-1,1]). The velocity is continuous along the cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuousity
$\tau$ of the tracers at the cross section. This graph is not continuous
and the jumps in $\tau$ mean that the initial neighbor tracers have been
seperated by the bodies.

In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of $\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in Fig.~\ref{fig:Eroding20tort_traj}
if the difference of length of the neighboring trajectories is large. From Fig.~\ref{fig:Eroding20tort_traj},
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
The pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
are splitted by three close bodies. 
}

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/erodingspeed20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
  touching eroding bodies and the eroding speed verse time.}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow.
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256 $}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The trajectories of 200 tracers in the fluid with 100 bodies}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

{\color{red} the definition of porosity is the ratio 
$$\phi=\frac{A_v}{A_T}$$
where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.

We define the local tortuosity
$$\tau(y)=\frac{\lambda(y)}{d}$$ 
of the tracers at $y$ on the starting cross section
where $\lambda(y)$ is the trajectory length of the tracer at y 
and $d$ is the distance from the starting cross section to 
the endding starting cross section. }

@@

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the endding starting cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field. In
Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighbor tracers have been
seperated by the bodies.

In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in 
Fig.~\ref{fig:Eroding20tort_traj}
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort_traj},
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
are splitted by three close bodies. 
}

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/erodingspeed20dense}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly
  touching eroding bodies and the eroding speed verse time. }
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies.
(a) The 
x-component velocity u(-1, y) with respect to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the cross section x = -1. 
(b) The local tortuosity $\tau(y)$ on the cross section x = -1.  }
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
In Fig.~\ref{fig:Eroding100vort}

In Fig.~\ref{fig:Eroding100tracer}

In Fig.~\ref{fig:Eroding100tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=3.9021
\times 10^{-4}$ at equal spreading tracers on the cross section (x=-1
and y in [-1,1]).

In Fig.~\ref{fig:Eroding100tort_traj}

}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256 $}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The trajectories of 200 tracers in the fluid with 100 bodies}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/velocity_loc100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/tort_local100}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/diff_tort100}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/uminDumax100}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding100tort} The tortuosity of the 100 bodies}
\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort100b_diff_top50}
\caption{\label{fig:Eroding100tort_traj} The largest 50 difference of the length of 
local tortuosity $\tau$ at two neighboring tracers in
100 bodies eroding. The same color of a pair of trajectories 
means they are from two neighboring tracers.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
